# A quick look at BAAD

```{r, results="hide", echo=FALSE, message=FALSE}
knitr::opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="")

data <- baad$data
var_def <- baad$dictionary
vars <- setdiff(var_def$variable[var_def$type == "numeric"],
                c("map", "mat", "lai", "age"))
```
The Biomass And Allometry Database for woody plants (BAAD) contains `r sum(!is.na(data[,vars]))` measurements collected in `r length(unique(data$studyName))` different studies, from `r nrow(data)` individuals across `r length(unique(data$species))` species.


```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=7}
figure_map(baad)
```

**Figure 1** Global distribution of studies included in the BAAD. Symbols are sized relative to the number of individual plants in each dataset.

## Variables

**Number of observations by variable**

```{r results='asis', echo=FALSE, warning=FALSE}

kable(table_summary(baad), "markdown", align="l", padding=10)
```

## Some plots


```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=7}
figure_variable_count(baad)
```

**Figure 2** Plot of most commonly recorded variables in BAAD.


```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=7}
figure_allometry_LH(baad)
```

**Figure 3** Plot of leaf area vs height in BAAD.

For more info on the BAAD see the paper in [Ecology](http://doi.org/10.1890/14-1889.1) or the [github repo](https://github.com/dfalster/baad).
